Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
added hyperlink package and changed my color to red
very minor correction

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}                               
\usepackage[usenames,dvipsnames]{color}  
\usepackage{enumerate}

\newcommand{\dean}[1]{\textcolor{green}{#1}}
\newcommand{\parham}[1]{\textcolor{blue}{#1}}
% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}

@@

Equations \ref{eq:KernelExpansion} and \ref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem. In other words, the neural field must be band-limited up to a given spatial frequency.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}                               
\usepackage[usenames,dvipsnames]{color}  
%This bit is how to use hyperlink without stupid coloured rectangles around it
\usepackage{float}
\usepackage{hyperref}
\hypersetup{colorlinks,linkcolor=black,filecolor=black,urlcolor=black,citecolor=black}

\newcommand{\dean}[1]{\textcolor{green}{#1}}
\newcommand{\parham}[1]{\textcolor{red}{#1}}
% \newcommand{\mike}[1]{\textcolor{Plum}{#1}}

@@

Eqs.~\eqref{eq:KernelExpansion} and \eqref{eq:FieldExpansion} are infinite series expansions and must be truncated to some level $j,$ in order to solve the estimation problem. In other words, the neural field must be band-limited up to a given spatial frequency.
